N-Body problem

### 2014-10-25 article/article.tex
implementation section

attachment

>>>>

The simulation was implemented in a C++11 application, with SDL2 and OpenGL for the visualisation. Calculations have been done with single precision floating point math, though the application is programmed in such a way that it is relatively easy to change this to double precision floating point math later. \\\\
The implementation uses sequential (i.e. non-parallel) code to implement the studied n-body simulation algorithms. Data was written to textfiles and analyzed using R and Gnuplot.
